Effects of rotation on the Lyman-$\alpha$ line morphology in distant galaxies

### 2013-04-11 paper/Analisis.tex
afiliacion

\title[Rotation in the Lyman-$\alpha$ line]{Effects of rotation on the
  Lyman-$\alpha$ line morphology in distant galaxies}
\author[N. Garavito and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Nicolas Garavito-Camargo.$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$Uni A
$^{2}$Uni B
}
\maketitle

\begin{abstract}

@@

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{Width7Central.png}
    \includegraphics[width=0.45\textwidth]{Width7Homogeneous.png}
    \includegraphics[width=0.45\textwidth]{Width6.png}
    \includegraphics[width=0.45\textwidth]{Width6HOM.png}
    \includegraphics[width=0.45\textwidth]{Width5.png}
    \includegraphics[width=0.45\textwidth]{Width5HOM.png}
\caption{Width of the lyman-alpha line for all the models.   \label{fig:widthvsvelocity}}
\end{figure*}

@@

@@

@@

We have seen in the previous section that rotation affects the number
of scatterings that

The fraction of photons that escape from the cloud of gas and dust is
defined as:\\

@@

Where NI is the initial number of photons and NF is the final,
$\vec{k}$ is the rotation axis direction and $\vec{o}$ the observer
direction. With this definition we compute the escape fraction for all
of our models, the results are shown in Fig ~\ref{figure:escape}\\

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{FECentral5.png}
  \includegraphics[width=0.45\textwidth]{FEHOM5.png}
  \includegraphics[width=0.45\textwidth]{FECentral6.png}
  \includegraphics[width=0.45\textwidth]{FEHOM6.png}
  \includegraphics[width=0.45\textwidth]{FECentral7.png}
  \includegraphics[width=0.45\textwidth]{FEHOM7.png}
  \label{figure:escape}\caption{Escape fraction for all the models. Left
    panels show the central distribution, while right panels show the
    homogeneous distribution} 
\end{figure*}

We found that for the central distribution the escape fraction does
not depend in velocity neither in the angle of observation, while it
does in the optical depth, this result was already known from previous
works (references). On the other hand for the homogeneous distribution
we found that for higher velocities photons escape easily. The
difference between this two results is due to the fact that in the
homogeneous distribution photons are emitted closer to the escape
surface and this makes this configuration more sensitive to
rotation. This last argument also explain the fact that in the
homogeneous distribution the optical depth does not affects the escape
fraction .

>>>>

\title[Rotation in the Lyman-$\alpha$ line]{Effects of rotation on the
  Lyman-$\alpha$ line morphology in distant galaxies}
\author[N. Garavito and J.E. Forero-Romero]{
\parbox[t]{\textwidth}{\raggedright 
  Nicolas Garavito-Camargo.$^{1}$ 
  Jaime E. Forero-Romero$^{2}$ 
}
\vspace*{6pt}\\
$^{1}$Universidad de los Andes
$^{2}$Uni B
}
\maketitle

\begin{abstract}
Rotation is present in the gas kinematics of galaxies up to the
highest redshifts. In this paper we present for the first time
radiative transfer calculations that show the impact of rotation on
the morphology of the Lyman $\alpha$ line. To this end we construct
simplified models where a galaxy is modeled as an homogeneous sphere
composed as an homogenous mixture of dust and hydrogen at a constant
temperature. These spheres have an solid-body rotation with linear
velocities at the surface in the range $0-300$ \kms. We consider
radiation sources both in the center of the rotating cloud and also
homogeneously distributed around the sphere. We find that higher
rotational velocities increase the width of each peak in the outgoing
line profile while it also increases the amount of Lyman alpha photons
escaping in the line center. This trends makes that for high
rotational velocities and large Hydrogen optical depths the double
peak of the line tends to be erased an be replaced by a single peak the
lines center. This is more pronounced for radiation sources
homogeneously distributed. Concerning the escape fraction we find that
rotation does not have any effect, provided that all the sources are
centrally emitted. However in the case of homogeneously emitted
sources we measure an increase of about a factor of $2$ in the escape
fraction for higher rotational velocity vealues.

Our work shows clearly that gas rotation has a non
negligeable impact on the shape of the Lyman $\alpha$ line.

@@

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{WidthCentral.png}
    \includegraphics[width=0.45\textwidth]{WidthHomogeneous.png}
   \caption{Width of the lyman-alpha line for all the models.   \label{fig:widthvsvelocity}}
\end{figure*}

@@

\begin{figure*}
    \includegraphics[width=0.45\textwidth]{maximumvscosthetaHOMSameSpeed.png}
    \includegraphics[width=0.45\textwidth]{maximumvscosthetaDifSpeedCentral.png}
\caption{Position of the maxima
    in the outgoing spectra for differents Rotational velocities,
    (up)Central Distriution, (Down) Homogeneous Distribution.\label{fig:maximumsvsvelocity}} 
\end{figure*}

@@

as we think Nscatt is related with the double peacked line and maxima positions

\begin{figure*}[ht]
    \includegraphics[width=0.45\textwidth]{NscattCentral.png}
    \includegraphics[width=0.45\textwidth]{NscattHOM.png}
\caption{Nscatt\label{fig:Nscatt}} 
\end{figure*}

@@

We have seen in the previous section that rotation affects the number
of scatterings that ..\\

Of particular interest is to compute the escape fraction of Lyman $\alpha$ photons coming from the most distant galaxies, due to the fact that with the observed intensity of the lyman alpha line quantities as the LF and SFR can be derived (put some references). \\

Previous studies have shown the correlation of the Escape fraction with galctic mass (Lauren 2009 et al, Dayal et al 2010) abundacies and the kinematics of dust. In order to study pure rotational effects in the escape fraction we fixed the dust abundance $\tau_{A}=0.01$ and the galaxy mass. We compute the escape fraction for the models described in Table \ref{table:models}.\\

For a realistic model we also take into account the viewing angle, first we fixed the viewing angle at $\theta = 0$  Fig. and then we fixed the velocity in order to see the escape fraction correlation with the viewing angle. Therefore we define the escape fraction as:\\

@@

Where NI is the initial number of photons and NF is the final,
$\vec{k}$ is the rotation axis direction and $\vec{o}$ the observer
direction. With this definition we compute the escape fraction for all
of our models, the results are shown in Fig \ref{figure:escape}\\

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{FECENTRAL.png}
  \includegraphics[width=0.45\textwidth]{FEHOMOGENEOUS.png}
   \label{figure:efvsv}\caption{Escape fraction for all the models. Left
    panels show the central distribution, while right panels show the
    homogeneous distribution} 
\end{figure*}

In Figure \ref{figure:efvsv} we found that in the central distribution the escape fraction does not change with velocity while it
does in the optical depth. On the other hand for the homogeneous distribution
we found that for higher velocities photons escape easily. The
difference between this two results relly in the fact that in the
homogeneous distribution photons are emitted closer to the escape
surface and this makes this configuration more sensitive to
rotation while in the central configuration the escape fraction depends mainly in the amount of gas rather than in rotation.

\begin{figure*}
  \includegraphics[width=0.45\textwidth]{FEHomogeneousvsThetaL.png}
 \label{figure:efvstheta}\caption{Escape fraction dependency with the viewing angle in the homogeneous configuration.} 
\end{figure*}
